Note on: Out-of-Sample Error for Laplacian Eigenmaps

### 2021-03-17 manuscripts/laplacian_eigenmaps/appendix.tex
Edited Section 2 Laplacian Eigenmaps manuscript.

In more detail, recall from our discuss.on in Section~\ref{subsec:analysis} that an essential step in our proofs is relating the iterated non-local operator $L_{P,\varepsilon}^j$ to the weighted Laplace-Beltrami operator $\Delta_P^j$, for $j = \floor{s/2}$. Suppose for the moment $s = 4$. Then we relate $L_{P,\varepsilon}$ to $\Delta_P$ by means of an intermediary nonlocal operator, as described by the following chain of estimates:
	\begin{align*}
	L_{P,\varepsilon} f(x) & = \int_{\mc{X}} \bigl(f(z) - f(x)\bigr)\eta\biggl(\frac{|z - x|}{\varepsilon}\biggr) \,dP(x) \\
	& = \bigl(1 + O(\varepsilon^2)\bigr) \int_{\mc{X}} \bigl(f(z) - f(z)\bigr)\eta\biggl(\frac{d_{\mc{X}}(z,x)}{\varepsilon}\biggr) \,dP(x) \\
	& = \Delta_Pf(x) + O\bigl(\varepsilon^2M\bigr) + O(\varepsilon^3).
	\end{align*}
	Here, $d_{\mc{X}}(\cdot,\cdot)$ is the geodesic distance on $\mc{X}$. For simplicity we have assumed $f \in C^3(\mc{X})$ and $p \in C^2(\mc{X})$, but the main idea will not change if we assume Sobolev smoothness instead. From this, we may deduce that
	\begin{align*}
	L_{P,\varepsilon}^2 f(x) = 
	\end{align*}
	When $s = 1$, this suffices.

>>>>

\paragraph{Discussion of requirements that $s \leq 3$.}
Recall from our discussion in Section~\ref{subsec:analysis} that an essential step in the proof of Lemma~\textcolor{red}{(?)}---which establishes a high-probability upper bound on $\dotp{L_{n,\varepsilon}^sf_0}{f_0}_n$---is relating the iterated non-local operator $L_{P,\varepsilon}^j$ to the weighted Laplace-Beltrami operator $\Delta_P^j$, for $j = \floor{s/2}$. Suppose for the moment $s = 3$, and $f \in C^3(\mc{X};1)$ and $p$ is uniform. In this case $\floor{s/2} = 1$, and the relation between $L_{P,\varepsilon}$ to $\Delta_P$ has been worked out by \textcolor{red}{(Burago2013, GarciaTrillos2019, Calder2019, GarciaTrillos2020)}. This relation is accomplished by means of an intermediary nonlocal operator, as described by the following chain of estimates:
\begin{align*}
L_{P,\varepsilon} f(x) & = \frac{1}{\varepsilon^{m + 2}}\int_{\mc{X}} \bigl(f(z) - f(x)\bigr)\eta\biggl(\frac{\|z - x\|}{\varepsilon}\biggr) \,d\mu(z) \\
& \overset{(i)}{=} \frac{1}{\varepsilon^{m + 2}} \int_{\mc{X}} \bigl(f(z) - f(x)\bigr)\eta\biggl(\frac{d_{\mc{X}}(z,x)}{\varepsilon}\biggr) \,d\mu(z) + O(\varepsilon) \\
& = \frac{1}{\varepsilon^{m + 2}} \int_{T_x(\mc{X})} \Bigl(f\bigl(\exp_x(v)\bigr) - f\bigl(\exp_x(0)\bigr)\Bigr)\eta\biggl(\frac{d_{\mc{X}}\bigl(\exp_x(v),\exp_x(0)\bigr)}{\varepsilon}\biggr) J_x(v) \,dv + O(\varepsilon) \\
& \overset{(ii)}{=} \frac{1}{\varepsilon^{m + 2}} \int_{T_x(\mc{X})} \Bigl(f\bigl(\exp_x(v)\bigr) - f\bigl(\exp_x(0)\bigr)\Bigr)\eta\biggl(\frac{d_{\mc{X}}\bigl(\exp_x(v),\exp_x(0)\bigr)}{\varepsilon}\biggr) \,dv + O(\varepsilon) \\
& = \frac{1}{\varepsilon^{m + 2}} \int_{T_x(\mc{X})} \Bigl(f\bigl(\exp_x(v)\bigr) - f\bigl(\exp_x(0)\bigr)\Bigr)\eta\biggl(\frac{\|v\|}{\varepsilon}\biggr) \,dv + O(\varepsilon) \\
& \overset{(iii)}{=} \Delta_Pf(x) + O(\varepsilon)
\end{align*}
Here, $d_{\mc{X}}(\cdot,\cdot)$ is the geodesic distance on $\mc{X}$, $J_x(v)$ denotes the Jacobian of the exponential map $\exp_x$ evaluated at $v \in T_x(\mc{M})$, and $h = f \circ \exp_x$. Then $(i)$ follows because $\bigl|d_{\mc{X}}(x,z)  - \|z - x\|\bigr| = O(\varepsilon^3)$ and $\eta$ is a Lipschitz function with bounded Lipschitz constant, $(ii)$ follows because the Jacobian $J_x(v)$ satisfies $|J_x(v)| = 1 + O(\varepsilon^2)$ for all $v \in B(0,\varepsilon) \subset T_x(\mc{X})$, and $(iii)$ follows since the function $h$ admits the Taylor expansion
\begin{equation*}
h(v) = h(0) + \dotp{\nabla h(0)}{v} + \frac{1}{2} \dotp{\nabla^2 h(0) v}{v} + O(\varepsilon^3),~~\textrm{for all $v \in B(0,\varepsilon) \subset T_x(\mc{X})$.}
\end{equation*}
Then, using the upper bound on $\max_{i = 1,\ldots,n}|L_{n,\varepsilon}f(X_i) - L_{P,\varepsilon}(X_i)| = O_\Pbb((n\varepsilon^{m + 4})^{-1})$ given in \textcolor{red}{(?)}, and the fact that $\Delta_Pf \in C^1(\mc{X};1)$, we have that,
\begin{align*}
\dotp{L_{n,\varepsilon}^3f}{f}_n & = \frac{1}{n^2 \varepsilon^{m + 2}} \sum_{i,j = 1}^{n} \bigl(L_{n,\varepsilon}f(X_i) - L_{n,\varepsilon}f(X_j)\bigr)^2 \eta\biggl(\frac{\|X_i - X_j\|}{\varepsilon}\biggr) \\
& = \frac{1}{n^2 \varepsilon^{m + 2}} \sum_{i,j = 1}^{n} \bigl(L_{P,\varepsilon}f(X_i) - L_{P,\varepsilon}f(X_j)\bigr)^2 \eta\biggl(\frac{\|X_i - X_j\|}{\varepsilon}\biggr) + O_{\Pbb}\biggl(\frac{1}{n\varepsilon^{m + 4}}\biggr) \\
& = \frac{1}{n^2 \varepsilon^{m + 2}} \sum_{i,j = 1}^{n} \bigl(\Delta_Pf(X_i) - \Delta_Pf(X_j)\bigr)^2 \eta\biggl(\frac{\|X_i - X_j\|}{\varepsilon}\biggr) + O_{\Pbb}\biggl(\frac{1}{n\varepsilon^{m + 4}}\biggr) + O_{\Pbb}(1) \\
& = O_{\Pbb}\biggl(\frac{1}{n\varepsilon^{m + 4}}\biggr) + O_{\Pbb}(1) = O_{\Pbb}(1),
\end{align*}
with the last equality following when $\varepsilon = \Omega(n^{-1/(m + 4)})$.

On the other hand when $s = 4$, and thus $j = 2$, we have only that
\begin{equation*}
L_{P,\varepsilon}^2f(x) = L_{P,\varepsilon}(\Delta_Pf + O(\varepsilon)) = \Delta_P^2f(x) + O(1/\varepsilon),
\end{equation*}
which is useless when $\varepsilon \to 0$. The bottom line is that in the manifold case, the $O(\varepsilon^3)$ error incurred by going between Euclidean norm and geodesic distance is negligible only when $j = 1$.

\section{Comparison of Laplacian eigenmaps and kernel smoothing in non-uniform density setting}

\textcolor{red}{(TODO)}
\begin{itemize}
	\item \textcolor{red}{Mention the relationship between the estimation problem under consideration and classification with a margin (Tsybakov noise) condition.}
\end{itemize}

### 2021-03-17 notes/weekly_notes/12.24.20.NotesForWeek.tex
Edited Section 2 Laplacian Eigenmaps manuscript.

\subsection{Proof of Lemma~\ref{lem:kernel_smoothing_bias}, $d = 1$ and $p \in C^k$.}
\label{subsec:kernel_smoothing_bias_pf_1d_smooth_p}
As in~\ref{subsec:kernel_smoothing_bias_pf_1d_uniform_p}, we take $\Omega = (0,1)$, let
\begin{equation*}
\|L_{P,\varepsilon}u\|_{P}^2 = \underbrace{\int_{\Omega_{\varepsilon}} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_1} + \underbrace{\int_{\partial_{\varepsilon}\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_2},
\end{equation*}
and turn to separately upper bounding $I_1$ and $I_2$.

\paragraph{Upper bound on $I_1$.}
We will show that for all $x \in \Omega_{\varepsilon}$,
\begin{equation*}
L_{P,\varepsilon}u(x) = \varepsilon^{k} \frac{\sigma_\eta}{k!}\Bigl( \frac{d^k}{dx^k}(up)(x) - p^{(k)}(x)u(x) + r(x)\Bigr)
\end{equation*}
for a remainder term $r$ satisfying $\int_{\Omega_{\varepsilon}} \bigl(r(x)\bigr)^2 p(x) \,dx  = o(1)$ as $\varepsilon \to 0$. This in turn will imply
\begin{align*}
I_1 = \int_{\Omega_{\varepsilon}} |L_{P,\varepsilon}u(x)|^2 \,dx & = \varepsilon^{2k} \frac{\sigma_\eta^2}{(k!)^2}\Bigl(\int_{\Omega_{\varepsilon}} \Bigl( \frac{d^k}{dx^k}(up)(x) - p^{(k)}(x)u(x) + r(x)\Bigr)^2  p(x) \,dx \\
& \leq 3 \varepsilon^{2k} \frac{\sigma_\eta^2}{(k!)^2} \bigl( |up|_{H^k(P)}^2 + |p^{(k)}u|_{\Leb^2(P)}^2 + o(1)\bigr) \\
& \leq C \varepsilon^{2k} \frac{\sigma_\eta^2}{(k!)^2} \Bigl( \|p\|_{C^k(P)}^2\bigl(|u|_{H^k(P)}^2 + |u|_{\Leb^2(P)}^2\bigr) + o(1) \Bigr),
\end{align*}
with the last line following from Young's inequality.

It remains to show the pointwise estimate \textcolor{red}{(...)}.

>>>>

\subsection{Proof of Lemma~\ref{lem:kernel_smoothing_bias}, $d = 1$ and $p \in C^k$.}
\label{subsec:kernel_smoothing_bias_pf_1d_smooth_p}
As in Section~\ref{subsec:kernel_smoothing_bias_pf_1d_uniform_p}, we take $\Omega = (0,1)$, let
\begin{equation*}
\|L_{P,\varepsilon}u\|_{P}^2 = \underbrace{\int_{\Omega_{\varepsilon}} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_1} + \underbrace{\int_{\partial_{\varepsilon}\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_2}.
\end{equation*}
We upper bound $I_2$ immediately, using~\eqref{pf:kernel_smoothing_bias_1d_2}, the equivalent upper bound when $p$ is uniform, to determine that
\begin{equation*}
I_2 \leq p_{\max}\int_{\partial_{\varepsilon}\Omega} |L_{P,\varepsilon}u(x)|^2 \,dx \leq C\varepsilon^{2k + 1}\|u^{(k)}\|_P^2.
\end{equation*}
It therefore remains only to upper bound $I_1$.

\paragraph{Upper bound on $I_1$.}
The $k$th order Taylor expansion of $u$ is
\begin{equation}
\label{pf:kernel_smoothing_bias_1d_smooth_p_1}
u(z) - u(x) = \sum_{j = 1}^{k - 1}\frac{1}{j!} u^{(j)}(x) (z - x)^j + (z - x)^k r_z^{(k)}(x;u).
\end{equation}
The $k-1$st order Taylor expansion of $p$ is
\begin{equation}
\label{pf:kernel_smoothing_bias_1d_smooth_p_2}
p(z) = \sum_{j = 0}^{k - 2}\frac{1}{j!} p^{(j)}(x) (z - x)^j + (z - x)^{k - 1} r_z^{(k - 1)}(x;p).
\end{equation}
Note that we adopt the convention that if $i > j$, then $\sum_{i}^{j} a_i = 0$, to cover the case when $k = 1$. Also, for a given $j \in \mathbb{N}$ and $j$ times differentiable function $f$, we have written $r_z^{(j)}(x;f)$ for the $j$th order remainder term,
\begin{equation*}
r_z^{(j)}(x;f) = \frac{1}{j!}\int_{0}^{1} (1 - t)^{j - 1} f^{(j)}(x + t(z - x)) \,dt.
\end{equation*}
Now, we plug the expressions~\eqref{pf:kernel_smoothing_bias_1d_smooth_p_1} and~\eqref{pf:kernel_smoothing_bias_1d_smooth_p_2} in to the definition of $L_{P,\varepsilon}u(x)$ as follows (let $\ell = k - 1$ for simplicity):
\begin{align}
d_P(x) \cdot L_{P,\varepsilon}u(x) & = \int_{\Omega} (u(z) - u(x)) \eta\biggl(\frac{z - x}{\varepsilon}\biggr) p(z) \,dz \nonumber \\
& = \sum_{j = 1}^{\ell} u^{(j)}(x) \int_{\Omega} (z - x)^j \eta\biggl(\frac{z - x}{\varepsilon}\biggr) p(z) \,dz + \int_{\Omega} (z - x)^{k} r_z^{(k)}(x;u) \eta\biggl(\frac{z - x}{\varepsilon}\biggr) p(z) \,dx \nonumber \\
& = \sum_{j_1 = 1}^{\ell} \sum_{j_2 = 0}^{\ell - 1} \frac{u^{(j_1)}(x) p^{(j_2)}(x)}{j_1!j_2!} \int_{\Omega} (z - x)^{j_1 + j_2} \eta\biggl(\frac{z - x}{\varepsilon}\biggr) p(z) \,dz + \sum_{j = 1}^{\ell} u^{(j)}(x) \int_{\Omega} (z - x)^{j + \ell} r_z^{(\ell)}(x;p) \,dz \nonumber \\
& ~~ + \int_{\Omega} (z - x)^{k} r_z^{(k)}(x;u) \eta\biggl(\frac{z - x}{\varepsilon}\biggr) p(z) \nonumber \\
& =: T_1(x) + T_2(x) + T_3(x). \label{pf:kernel_smoothing_bias_1d_smooth_p_3}
\end{align}

By Assumptions~\ref{asmp:domain} and~\ref{asmp:density}, we have that $|d_P(x)| \geq p_{\min} \alpha\varepsilon$ for all $x \in \Omega$. It will therefore suffice to show the following upper bounds
\begin{equation}
\label{pf:kernel_smoothing_bias_1d_smooth_p_4}
\|T_i\|_{\Omega_{\varepsilon}}^2 \leq C_i \varepsilon^{2(k + 1)} \|u\|_{H^{k}(P)}^2
\end{equation}
for $i = 1,2,3$, since along with~\eqref{pf:kernel_smoothing_bias_1d_smooth_p_3} this will imply
\begin{equation*}
I_1 \leq \frac{3p_{\max}}{\alpha^2 p_{\min}^2 \varepsilon^2} \sum_{i = 1}^{3} C_i \varepsilon^{2(k + 1)} \|u\|_{H^{k}(P)}^2 = C \varepsilon^{2k} \|u\|_{H^k(P)}^2.
\end{equation*}
We now establish~\eqref{pf:kernel_smoothing_bias_1d_smooth_p_4} for each of $i = 1,2,3$.

\textit{Upper bound on $\|T_1\|_{\Omega_{\varepsilon}}^2$.}
We introduce some notation to keep our formulae as readable as possible. Let $[k] = \{1,\ldots,k\}$ and let $\mathbf{J} := \bigl\{(j_1,j_2): j_1 \in [\ell], j_2 \in [\ell - 1] \cup \{0\}, j_1 + j_2 \geq k\bigr\}$. Note that if $j_1 \in [\ell]$ and $j_2 \in [\ell - 1] \cup \{0\}$ do not satisfy $(j_1,j_2) \in \mathbf{J}$, then the order-$s$ property of $\eta$ combined with the fact $B(x,\varepsilon) \in \Omega$ implies that
\begin{equation*}
\int_{\Omega} (z - x)^{j_1 + j_2} \eta\biggl(\frac{z - x}{\varepsilon}\biggr) p(z) \,dz = 0.
\end{equation*}
On the other hand if $(j_1,j_2) \in \mathbf{J}$ then by a change of variables
\begin{equation*}
\int_{\Omega} (z - x)^{j_1 + j_2} \eta\biggl(\frac{z - x}{\varepsilon}\biggr) p(z) \,dz = \varepsilon^{j_1 + j_2} \int_{B(0,1)} v^{j_1 + j_2 + 1} \eta(|v|) \,dv =: \varepsilon^{j_1 + j_2 + 1} \sigma_\eta^{(j_1 + j_2)},
\end{equation*}
with Assumption~\ref{asmp:kernel} guaranteeing that $\sigma_\eta^{(j)} < \infty$ for all $j \in \mathbb{N}$. Therefore,
\begin{equation*}
T_1(x) = \sum_{(j_1,j_2) \in \mathbf{J}} \frac{\varepsilon^{j_1 + j_2 + 1}}{j_1!j_2!} u^{(j_1)}(x) p^{(j_2)}(x) .
\end{equation*}
Next, we note that by H\"{o}lder's inequality, $\|u^{(j_1)} p^{(j_2)} \|_{\Omega_{\varepsilon}}^2 \leq  \|p^{(j_2)}\|_{L^{\infty}(\Omega_{\varepsilon})}^2 \|u^{(j_1)}\|_{\Omega_{\varepsilon}}^2 \leq \|u\|_{H^k(\Omega)}^2$. As a result,
\begin{equation*}
\|T_1\|_{\Omega_{\varepsilon}}^2 \leq |\mathbf{J}| \cdot \sum_{(j_1,j_2) \in \mathbf{J}} \frac{\varepsilon^{2(j_1 + j_2 + 1)}}{(j_1!j_2!)^2} \|p^{(j_1)}  u^{(j_2)}\|_{\Omega_{\varepsilon}}^2 \leq \frac{1}{(k - 1)!} \varepsilon^{2(k + 1)} \|u\|_{H^k(\Omega)}^2,
\end{equation*}
and thus~\eqref{pf:kernel_smoothing_bias_1d_smooth_p_3} follows with $C_1 = 1/(k - 1)!$.

\textit{Upper bound on $\|T_2\|_{\Omega_{\varepsilon}}^2$.}
Note that if $k = 1$ then $T_2(x) = 0$, so that we need only cover the case where $k > 1$. In this case, observe that since $p \in C^{\ell}(P;1)$, it follows that $|r_z^{(\ell)}(x;p)| \leq 1/\ell!$ for all $z \in B(x,\varepsilon)$, and thus by H\"{o}lder's inequality,
\begin{equation*}
\biggl|\int_{\Omega} (z - x)^{j + \ell} r_z^{(\ell)}(x;p) \eta\biggl(\frac{z - x}{\varepsilon}\biggr) \,dz\biggr| \leq \varepsilon^{j + \ell}\int_{\Omega} \biggl| \eta\biggl(\frac{z - x}{\varepsilon}\biggr) \biggr| \,dz \leq \|\eta\|_{\infty} \nu_1 \varepsilon^{j + \ell + 1} 
\end{equation*}
for any $j \in \mathbb{N}$. An upper bound on $|T_2(x)|$ follows immediately,
\begin{equation*}
|T_2(x)| \leq \sum_{j = 1}^{\ell} \biggl|\frac{u^{(j)}(x)}{j!}\biggr| \biggl|\int_{\Omega} (z - x)^{j + \ell} r_z^{(\ell)}(x;p) \eta\biggl(\frac{z - x}{\varepsilon}\biggr) \,dz\biggr| \leq \|\eta\|_{\infty} \nu_1 \varepsilon^{k + 1} \sum_{j = 1}^{\ell} \frac{|u^{(j)}(x)|}{j!\ell!}.
\end{equation*}
and calculations similar to above imply that
\begin{equation*}
\|T_2\|_{\Omega_{\varepsilon}}^2 \leq \biggl(\frac{\|\eta\|_{\infty} \nu_1}{(\ell - 1)!}\biggr)^2 \varepsilon^{2(k + 1)} \|u\|_{H^k(\Omega)}^2,
\end{equation*}
and thus~\eqref{pf:kernel_smoothing_bias_1d_smooth_p_3} follows with $C_2 = \|\eta\|_{\infty} \nu_1/(\ell - 1)!$.

\textit{Upper bound on $\|T_3\|_{\Omega_{\varepsilon}}^2$.}
We begin by upper bounding $|T_3(x)|$ for any $x \in \Omega_{\varepsilon}$. Using the change of variables $v = (z - x)/\varepsilon$, we determine that
\begin{equation*}
|T_3(x)| \leq \int_{\Omega} \biggl| (z - x)^{k} r_z^{(k)}(x;u) \eta\biggl(\frac{z - x}{\varepsilon}\biggr)  p(z) \biggr|\,dz  \leq \varepsilon^{k + 1} \|\eta\|_{\infty} p_{\max} \int_{B(0,1)} \Bigl|r_{x + \varepsilon v}^{(k)}(x;u)\Bigr| \,dv.
\end{equation*}
From here, using the Cauchy-Schwarz inequality twice, we obtain the following upper bound on $\|T_3\|_{\Omega_{\varepsilon}}^2$,
\begin{align*}
\|T_3\|_{\Omega_{\varepsilon}}^2 & \leq (\|\eta\|_{\infty} p_{\max})^2 \varepsilon^{2(k + 1)} \int_{\Omega_{\varepsilon}}\biggl(\int_{B(0,1)} \Bigl|r_{x + \varepsilon v}^{(k)}(x;u)\Bigr| \,dv\biggr)^2 \,dx \\
& \leq (\|\eta\|_{\infty} p_{\max} \nu_1)^2 \varepsilon^{2(k + 1)} \int_{\Omega_{\varepsilon}} \int_{B(0,1)}\Bigl|r_{x + \varepsilon v}^{(k)}(x;u)\Bigr|^2 \,dv \,dx \\
& \leq \biggl(\frac{\|\eta\|_{\infty} p_{\max} \nu_1}{(k - 1)!}\biggr)^2 \varepsilon^{2(k + 1)} \int_{\Omega_{\varepsilon}} \int_{B(0,1)} \int_{0}^{1} \bigl|u^{(k)}\bigl(x + t\varepsilon v\bigr)\bigr|^2 \,dv \,dx.
\end{align*}
Finally, exchanging the order of integration gives
\begin{equation*}
\|T_3\|_{\Omega_{\varepsilon}}^2 \leq \biggl(\frac{\|\eta\|_{\infty} p_{\max}}{(k - 1)!}\biggr)^2 \nu_1 \varepsilon^{2(k + 1)} \|u\|_{H^k(\Omega)}^2,
\end{equation*}
and thus~\eqref{pf:kernel_smoothing_bias_1d_smooth_p_3} follows with $C_3 = (\|\eta\|_{\infty} p_{\max}/(k - 1)!)^2 \nu_1$.

\textcolor{red}{(TODO)}
\begin{itemize}
	\item \textcolor{red}{Equation~\eqref{pf:kernel_smoothing_bias_1d_smooth_p_3} is not well formatted}.
	\item \textcolor{red}{Need to define the norm used on the left hand side of  Equation~\eqref{pf:kernel_smoothing_bias_1d_smooth_p_4}}.
\end{itemize}

\section{Proof of Lemma~\ref{lem:kernel_smoothing_bias}}
Letting $\Omega_{\varepsilon} = \{x: B(x,\varepsilon) \subset \Omega\}$ and $\partial_{\varepsilon}\Omega = \Omega \setminus \Omega_{\varepsilon}$, we have that 
\begin{equation*}
\|L_{P,\varepsilon}u\|_P^2 = \underbrace{\int_{\Omega_{\varepsilon}} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_1} + \underbrace{\int_{\partial_{\varepsilon}\Omega} \bigl(L_{\varepsilon,P}u(x)\bigr)^2 \,dP(x)}_{:=I_2}
\end{equation*}
We will separately upper bound $I_1$---using the higher order property of $\eta$---and $I_2$---using the zero-trace property of $u$ and its $1$st up through $j - 1$st order derivatives.

\paragraph{Upper bound on $I_1$.}

\paragraph{Upper bound on $I_2$.}
